---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# COSTmos

<!-- badges: start -->
<!-- badges: end -->

COSTmos collates and displays reference data sets on healthcare costs in England. These are displayed in a Shiny dashboard and available as data frames within the package.

Data sets included are:  
- [Drug Tariff](https://www.nhsbsa.nhs.uk/pharmacies-gp-practices-and-appliance-contractors/drug-tariff)  
- [Prescription Cost Analysis](https://www.nhsbsa.nhs.uk/statistical-collections/prescription-cost-analysis-england)  
- [National Cost Collection](https://www.england.nhs.uk/costing-in-the-nhs/national-cost-collection/)  
- [Unit Costs of Health and Social Care](https://research.kent.ac.uk/corec/unit-costs-2022-2027/)  

COSTmos tries to display the latest version of the data sets. However, we recommend that you go to the original source to verify that this is the case.

## Installation

You can install the development version of COSTmos from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NICE-Data-and-Analytics/COSTmos")
```

## Running the COSTmos dashboard locally  

To run the COSTmos dashboard locally:  

```{r example, eval = FALSE}
library(COSTmos)

costmos_app()
```

## Using the datasets in COSTmos

The following datasets can be accessed after attaching COSTmos:

```{r, echo = FALSE}
list.files(rprojroot::find_package_root_file("data"), ".rda") |> 
  stringr::str_subset("version", negate = TRUE) |> 
  stringr::str_remove("\\.rda$")
```
View them using:

```{r, eval = FALSE}
library(COSTmos)

drug_tariff_ix

# View the help file
?drug_tariff_ix 
```

## References  

```{r, echo = FALSE}
data("drug_tariff_version")
```

```{r, child=c(rprojroot::find_package_root_file("inst", "references.Rmd"))}
```
